\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\usepackage[paperwidth=8.5in,paperheight=11in]{geometry}
\geometry{verbose,tmargin=0.5in,bmargin=1in,lmargin=1in,rmargin=1in}
\providecommand{\alert}[1]{\textbf{#1}}

\title{Guide to Report Writing}
%\author{G. Jay Kerns}
\date{\vspace{-0.5in}}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs Org-mode version 7.8.02}}

\begin{document}

\maketitle

\thispagestyle{empty}

\section*{Executive Summary}
\label{sec-1}

(one page brief description of the study and conclusion)
\section*{Introduction}
\label{sec-2}

\begin{itemize}
\item What is the question?
\item Why is the question important?
\item What are the hypotheses?
\item What is the type of study? (observational, experimental)
\item What is the type of analysis? (one sample t-test, paired-sample t-test, ANOVA, chi-square test, regression, \ldots{})
\end{itemize}
\section*{Describe data collection techniques}
\label{sec-3}

\begin{itemize}
\item Describe data collection procedures
\item Discuss limitations of data collection procedure
\end{itemize}
\section*{Summary Information}
\label{sec-4}

\begin{itemize}
\item Numeric Summary
\begin{itemize}
\item Discrete – frequency, percent, contingency tables, etc.
\item Continuous – mean, SD, Q1, Q3, etc.
\end{itemize}
\item Visual Summary
  +Side by Side Box Plots, Scatter Plots, Probability Plots, etc.
\end{itemize}
\section*{Analysis}
\label{sec-5}

\begin{itemize}
\item State hypothesis
\item Give test statistic and p-value (or Confidence Interval)
\item Interpret results
\item Attach tables and/or graphs and make reference to them in your report when necessary.
\end{itemize}
\section*{Conclusions}
\label{sec-6}

\begin{itemize}
\item Summarize Results
\item Discuss limitations of the study
\item Discuss possible further research
\end{itemize}

\end{document}